---
title: "R Notebook"
output: html_notebook
---

I will try some "turtle" plots, which are like directed walks. See here: https://fronkonstin.com/2014/07/07/four-simple-turtle-graphs-to-play-with-kids/.

Load packages:
```{r}
library(ggforce)
library(MexBrewer)
library(tidyverse)
```

## Example 1

This is a simple example. The turtle takes steps of size 1 + 0.5 * i in the direction of angle * i _and then returns to the origin_ before taking another step:
```{r}
df <- data.frame(x = 0, y = 0)
#angle <- -89.5 * pi/180
angle <- -89.5 * pi/180

for(i in 1:150){
  df <- df %>%
    rbind(data.frame(x = (1 + 0.5 * i) * cos(angle * i),
                     y = (1 + 0.5 * i) * sin(angle * i)))
}
```

Plot the path:
```{r}
ggplot() +
  geom_path(data = df,
            aes(x, y)) + 
  coord_equal() + 
  theme_void()
```

Plot with polygons:
```{r}
#col_palette <- mex.brewer("Atentado")

ggplot() +
  geom_polygon(data = df %>%
                 #mutate(color = runif(n()), fill = color),
                 mutate(color = runif(n()), fill = color),
               aes(x, y)) + 
  #scale_fill_gradientn(colors = #col_palette) +
  coord_equal() + 
  theme_void()
```

In this variation, the length of the step is compounded at each step:
```{r}
df <- data.frame(x = 0, y = 0)
#angle <- -89.5 * pi/180
angle <- -89.5 * pi/180

for(i in 1:150){
  df <- df %>%
    rbind(data.frame(x = (1.01)^i * cos(angle * i),
                     y = (1.001)^i * sin(angle * i)))
}
```

Plot the path:
```{r}
ggplot() +
  geom_path(data = df,
            aes(x, y),
            size = 0) + 
  coord_equal() + 
  theme_void()
```

Plot with polygons:
```{r}
ggplot() +
  geom_polygon(data = df[2:nrow(df),],
               aes(x, y)) + 
  coord_equal() + 
  theme_void()
``` 

Plot as segments:
```{r}
ggplot() +
  geom_segment(data = df,
               aes(x, y, xend = 0, yend = 0),
               size = 0) + 
  coord_equal() + 
  theme_void()
```

Add a symbol at the end of the segment:
```{r}
ggplot() +
  geom_segment(data = df,
               aes(x, y, xend = 0, yend = 0),
               size = 0) + 
  geom_point(data = df %>%
               slice_sample(prop = 0.25) %>%
               mutate(size = runif(n(), 0, 10)),
             aes(x, 
                 y,
                 size = size)) + 
  scale_size(range = c(0, 5)) +
  coord_equal() + 
  theme_void() + 
  theme(legend.position = "none")
```
Create a second turtle path:
```{r}
df2 <- data.frame(x = 0, y = 0)
#angle <- -89.5 * pi/180
angle <- -49.5 * pi/180

for(i in 1:150){
  df2 <- df2 %>%
    rbind(data.frame(x = (1.003)^i * cos(angle * i),
                     y = (1.01)^i * sin(angle * i)))
}
```


Plot as segments:
```{r}
ggplot() +
  geom_segment(data = df2,
               aes(x, y, xend = 0, yend = 0),
               size = 0) + 
  coord_equal() + 
  theme_void()
```

Bind data frames:
```{r}
df <- rbind(df,
            df2)
```

Add a symbol at the end of the segment:
```{r}
set.seed(356345)

df_sliced <- df %>%
  slice_sample(prop = 0.25) %>%
  mutate(size = runif(n(), 0, 10),
         color = factor(sample.int(3, n(), replace = TRUE)))

ggplot() +
  geom_segment(data = df,
               aes(x, y, xend = 0, yend = 0),
               alpha = 0.25,
               color = "black",
               size = 0) + 
  geom_point(data = df,
             aes(x, 
                 y),
             color = "black",
             size = 0.3) + 
  geom_point(data = df_sliced,
             aes(x, 
                 y,
                 size = size),
             color = "black") + 
  geom_point(data = df_sliced %>%
               mutate(size = 0.45 * size),
             aes(x, 
                 y,
                 size = size,
                 color = color)) + 
  scale_color_manual(values = c("1" = "#FF0000", "2" = "#0000FF", "3" = "#FFFF00")) +
  scale_size(range = c(1, 4)) +
  coord_equal() + 
  theme_void() + 
  theme(legend.position = "none",
        plot.background = element_rect(fill = "white"))
```

Pack it all:
```{r}
seed <- sample.int(100000, 1)
set.seed(seed)

df <- data.frame(x = 0, y = 0)
#angle <- -89.5 * pi/180
angle <- -89.5 * pi/180

step_f1 <- jitter(1, amount = 0.01)
step_f2 <- jitter(1, amount = 0.01)

n_1 <- round(runif(1, 70, 200))

for(i in 1:n_1){
  df <- df %>%
    rbind(data.frame(x = (step_f1)^i * cos(angle * i),
                     y = (step_f2)^i * sin(angle * i)))
}

df2 <- data.frame(x = 0, y = 0)
angle <- -49.5 * pi/180
step_f3 <- jitter(1, amount = 0.01)
step_f4 <- jitter(1, amount = 0.01)

n_2<- round(runif(1, 70, 250))

for(i in 1:n_2){
  df2 <- df2 %>%
    rbind(data.frame(x = (step_f3)^i * cos(angle * i),
                     y = (step_f4)^i * sin(angle * i)))
}

df <- rbind(df,
            df2)

palette_name <- sample(c("Alacena", "Atentado", "Aurora", "Concha", "Frida", "Revolucion", "Ronda", "Tierra"), 1)
col_palette <- mex.brewer(palette_name)

df_sliced <- df %>%
  slice_sample(prop = 0.25) %>%
  mutate(size = runif(n(), 0, 10),
         color = factor(sample.int(3, n(), replace = TRUE)))

ggplot() +
  geom_segment(data = df,
               aes(x, y, 
                   xend = 0, yend = 0),
               alpha = 0.25,
               color = "white",
               size = 0) + 
  geom_point(data = df,
             aes(x, 
                 y),
             color = "white",
             size = 0.75) + 
  geom_point(data = df_sliced,
             aes(x, 
                 y,
                 size = size),
             color = "white") + 
  geom_point(data = df_sliced %>%
               mutate(size = 0.45 * size),
             aes(x, 
                 y,
                 size = size,
                 color = color)) + 
  scale_color_manual(values = sample(col_palette, 3)) +
  scale_size(range = c(1, 5)) +
  coord_equal() + 
  theme_void() + 
  theme(legend.position = "none",
        plot.background = element_rect(color = NA, 
                                       fill = "black"))
```

## Example 2

This is another example. The turtle takes a step of size 0.9 * i and direction angle * i _and then return to the origin_ before taking another step:
```{r}
df <- data.frame(x = 0, y = 0)
#angle <- -89.5 * pi/180
angle <- 144.3 * pi/180

for(i in 1:150){
  df <- df %>%
    # Multiply the angle by 1.0 to get a star that shrinks
    rbind(data.frame(x = (0.95 * i) * cos(1.01 * angle * i),
                     y = (0.95 * i) * sin(1.01 * angle * i)))
}

# Notice the difference with this; the turtle does _not_return to the origin:
# for(i in 1:50){
#   df <- df %>%
#     rbind(df %>%
#             slice_tail() %>%
#             mutate(x = x + 0.9 * cos(angle * i),
#                    y = y + 0.9 * sin(angle * i)))
# }
```

Plot the path:
```{r}
ggplot() +
  geom_path(data = df,
            aes(x, y)) + 
  coord_equal() + 
  theme_void()
```

Plot with segments:
```{r}
seed <- sample.int(100000, 1)
set.seed(seed)
palette_name <- sample(c("Alacena", "Atentado", "Aurora", "Concha", "Frida", "Revolucion", "Tierra"), 1)
col_palette <- mex.brewer(palette_name)

df_sliced <- df %>%
  slice_sample(prop = 0.75) %>%
  mutate(size = runif(n(), 0, 10),
         color = factor(sample.int(3, n(), replace = TRUE)))

ggplot() +
  geom_segment(data = df,
               aes(x, y, xend = 0, yend = 0)) + 
  geom_point(data = df,
             aes(x, y),
             size = 0.75) +
  geom_point(data = df_sliced,
             aes(x, 
                 y,
                 size = size),
             color = "black") + 
  geom_point(data = df_sliced %>%
               mutate(size = 0.45 * size),
             aes(x, 
                 y,
                 size = size,
                 color = color)) + 
  scale_color_manual(values = sample(col_palette, 3)) +
  scale_size(range = c(1, 5)) +
  coord_equal() + 
  theme_void() + 
  theme(legend.position = "none",
        plot.background = element_rect(fill = "white"))
```

Plot with polygons:
```{r}
ggplot() +
  geom_polygon(data = df,
               aes(x, y)) + 
  coord_equal() + 
  theme_void()
```

Pack it all:
```{r}
seed <- sample.int(100000, 1)
set.seed(seed)

df <- data.frame(x = 0, y = 0)
#angle <- -89.5 * pi/180
angle <- 144.3 * pi/180

step_f <- jitter(0.95, 0.9)
angle_f <- jitter(0.95, 0.9)

for(i in 1:150){
  df <- df %>%
    # Multiply the angle by 1.0 to get a star that shrinks
    rbind(data.frame(x = (step_f * i) * cos(angle_f * angle * i),
                     y = (step_f * i) * sin(angle_f * angle * i)))
}

palette_name <- sample(c("Alacena", "Atentado", "Aurora", "Concha", "Frida", "Revolucion", "Ronda", "Tierra"), 1)
col_palette <- mex.brewer(palette_name)

df_sliced <- df %>%
  slice_sample(prop = 0.75) %>%
  mutate(size = runif(n(), 0, 10),
         color = factor(sample.int(3, n(), replace = TRUE)))

ggplot() +
  geom_segment(data = df,
               aes(x, y, 
                   xend = 0, yend = 0),
               alpha = 0.25,
               color = "black",
               size = 0) + 
  geom_point(data = df,
             aes(x, y),
             size = 0.75) +
  geom_point(data = df_sliced,
             aes(x, 
                 y,
                 size = size),
             color = "black") + 
  geom_point(data = df_sliced %>%
               mutate(size = 0.45 * size),
             aes(x, 
                 y,
                 size = size,
                 color = color)) + 
  scale_color_manual(values = sample(col_palette, 3)) +
  scale_size(range = c(1, 5)) +
  coord_equal() + 
  theme_void() + 
  theme(legend.position = "none",
        plot.background = element_rect(fill = "white"))
```

Notice the difference when the turtle does not return to the origin:
```{r}
df <- data.frame(x = 0, y = 0)
#angle <- -89.5 * pi/180
angle <- 89 * pi/180

for(i in 1:25){
  df <- df %>%
    rbind(df %>%
            slice_tail() %>%
            mutate(x = x + 0.9 * cos(angle * i),
                   y = y + 0.9 * sin(angle * i)))
}
```

Plot the path:
```{r}
ggplot() +
  geom_path(data = df,
            aes(x, y)) + 
  coord_equal() + 
  theme_void()
```

Plot with diagonals:
```{r}
#seed <- sample.int(100000, 1)
set.seed(NULL)
palette_name <- sample(c("Alacena", "Atentado", "Aurora", "Concha", "Frida", "Revolucion", "Tierra"), 1)
col_palette <- mex.brewer(palette_name)
col_fill <- sample(col_palette, 1)
x0 <- jitter(mean(df$x), 0.9)
y0 <- jitter(mean(df$y), 0.9)  
rad <- runif(1, 0.15, 0.65)

ggplot() +
  # geom_diagonal(data = df,
  #           aes(x, y, xend = 0, yend = 0),
  #           color = col_fill,
  #           size = 1) + 
  geom_circle(aes(x0 = x0, y0 = y0,
                  r = rad,
                  fill = col_fill),
              color = NA) + 
  geom_diagonal(data = df,
                aes(x, y, xend = 0, yend = 0),
                color = "white",
                size = 1) +
  coord_equal(xlim = c(x0 - rad, 
                       x0 + rad), 
              ylim = c(y0 - rad, 
                       y0 + rad)) + 
  theme_void() + 
  theme(legend.position = "none",
        plot.background = element_rect(fill = "white"))
```

Put all together; this is very similar to Ijeamaka Anyene's minimal radial patterns (https://github.com/Ijeamakaanyene/patterns):
```{r}
seed <- sample.int(100000, 1)
set.seed(seed)

# Initialize radius of circle
rad <- runif(1, 0.15, 0.90)

# Initialize the data frame
df <- data.frame(x = 0, y = 0)

# Initialize the angle; this parameter is important, if it coincides with some values it creates closed polygons
#angle <- -89.5 * pi/180
angle <- runif(1, 0, 180) * pi/180

for(i in 1:sample.int(50, 1)){
  df <- df %>%
    rbind(df %>%
            slice_tail() %>%
            mutate(x = x + rad * cos(angle * i),
                   y = y + rad * sin(angle * i)))
}

# Select palette at random
palette_name <- sample(c("Alacena", "Atentado", "Aurora", "Concha", "Frida", "Revolucion", "Tierra"), 1)
col_palette <- mex.brewer(palette_name)

# Select a color from the palette
col_fill <- sample(col_palette, 2)

# Jitter coordinates of circle
x0 <- jitter(mean(df$x), 0.9)
y0 <- jitter(mean(df$y), 0.9)  


# Strength of diagonal
s <- runif(1, 0.25, 0.75)

# Plot
ggplot() +
  geom_circle(aes(x0 = mean(df$x), y0 = mean(df$y),
                  r = rad/runif(1, 3/4, 5/4)),
              fill = col_fill[1],
              color = NA) + 
  geom_diagonal(data = df,
                aes(x, y, 
                    xend = 0, yend = 0,
                    size = stat(index),
                    alpha = stat(index)),
                color = col_fill[2],
                size = 1,
                strength = s) +
  coord_equal(xlim = c(mean(df$x) - rad, 
                       mean(df$x) + rad), 
              ylim = c(mean(df$y) - rad, 
                       mean(df$y)+ rad)) + 
  theme_void() + 
  theme(legend.position = "none",
        plot.background = element_rect(color = NA,
                                       fill = col_fill[2]))
```


## Example 3

This is example is a little bit more involved. The turtle takes a step of length d with direction angle = 90 degrees; it does not return to the origin, but from its current position it takes another step of length d with an angle of 90 + previous angle. After four such steps, it has walked in a square; the length and angle of the next step will change, and then the turtle walks in a square again:
```{r}
df <- data.frame(x = 0, y = 0)

# Initialize the size of the step
d <- 50
# Initialize the angle the turtle is facing
angle <- pi/2

for(i in 1:320){
  df <- df %>%
    rbind(df %>%
            # Take the last row in the data frame
            slice_tail() %>%
            # Starting from the last position, move a distance d with the designated angle 
            mutate(x = x + d * cos(angle),
                   y = y + d * sin(angle)))
  # Do four right turns (pi/2) and then the next angle will be instead of a right turn an angle of 75 degrees
  angle <- ifelse(i %% 4 == 0,
                  angle + 75 * pi/180,
                  angle + pi/2)
  # Do four steps of length d, and then the next step will be of length 0.95 * d
  d <- ifelse(i %% 4 == 0,
              0.95 * d,
              d)
}
```

Plot the path:
```{r}
ggplot() +
  geom_path(data = df,
            aes(x, y)) + 
  coord_equal() + 
  theme_void()
```

Plot with polygons:
```{r}
ggplot() +
  geom_polygon(data = df,
               aes(x, y)) + 
  geom_path(data = df,
            aes(x, y),
            color="black") + 
  coord_equal() + 
  theme_void()
```

A variation is as follows: the turtle does not return to the origin, but at each step the length of the step is compounded/discounted (depending on whether >1 or <1), and the angle transitions proportionally to the step:
```{r}
df <- data.frame(x = 0, y = 0)
for(i in 1:320){df <- df %>%
  rbind(df %>%
          slice_tail() %>%
          mutate(x = x + (0.9545)^i * cos(1.35 * i),
                 y=y + (0.95)^i * sin(1.35 * i)))}

ggplot()+
  geom_polygon(data = df,
               aes(x,
                   y)) + 
  coord_equal() +
  theme_void()
```

Smaller angles result in more steps around, i.e., polygons with more sides.

Try with multiple data frames:
```{r}
df <- data.frame(x = 0, y = 0)

# Initialize the size of the step
#d <- 50
# Initialize the angle the turtle is facing
#angle <- pi/2

for(i in 1:320){
  df <- df %>%
    rbind(df %>%
            # Take the last row in the data frame
            slice_tail() %>%
            # Starting from the last position, move a distance d with the designated angle 
            mutate(x = x + (0.95)^i * cos(1.55 * i),
                   y = y + (0.95)^i * sin(1.55 * i)))
}
```

```{r}
df2 <- data.frame(x = 0, y = 0)

# Initialize the size of the step
#d <- 50
# Initialize the angle the turtle is facing
#angle <- pi/2

for(i in 1:60){
  df2 <- df2 %>%
    rbind(df2 %>%
            # Take the last row in the data frame
            slice_tail() %>%
            # Starting from the last position, move a distance d with the designated angle 
            mutate(x = x + (0.9475)^i * cos(1.55 * i),
                   y = y + (0.9475)^i * sin(1.55 * i)))
}
```

```{r}
df3 <- data.frame(x = 0, y = 0)

# Initialize the size of the step
#d <- 50
# Initialize the angle the turtle is facing
#angle <- pi/2

for(i in 1:30){
  df3 <- df3 %>%
    rbind(df3 %>%
            # Take the last row in the data frame
            slice_tail() %>%
            # Starting from the last position, move a distance d with the designated angle 
            mutate(x = x + (0.945)^i * cos(1.55 * i),
                   y = y + (0.945)^i * sin(1.55 * i)))
}
```

Put all paths together
```{r}
df <- rbind(df %>%
              mutate(path = "1"),
            df2 %>%
              mutate(path = "2"),
            df3 %>%
              mutate(path = "3"))
```

Plot the paths:
```{r}
ggplot() +
  geom_path(data = df,
            aes(x, 
                y,
                color = path)) + 
  scale_color_manual(values = c("1" = "gray80", "2" = "gray40", "3" = "black")) +
  coord_equal(expand = FALSE) + 
  theme_void() +
  theme(legend.position = "none")
```

Plot with polygons:
```{r}
ggplot() +
  geom_polygon(data = df,
               aes(x, y)) + 
  # geom_path(data = df2,
  #           aes(x, y),
  #           color="white",
  #           size = 0.25) + 
  coord_equal() + 
  theme_void()
```

## And an extra with hilbert numbers

Also see this: https://fronkonstin.com/2016/02/01/going-bananas-with-hilbert/

Define a function for Hilbert:
```{r}
hilbert <- function(m, n, r){
  for (i in 1:n){
    tmp <- cbind(t(m), m+nrow(m)^2)
    m <- rbind(tmp, (2*nrow(m))^r-tmp[nrow(m):1,]+1)
  }
  m %>% 
    data.frame() %>%
    mutate(row = 1:n()) %>%
    pivot_longer(cols = starts_with("X"), 
                 names_to = "y",
                 names_prefix = "X",
                 names_transform = list(y = as.integer),
                 values_to = "order") %>% 
    rename(x = row) %>%
    arrange(order)
}
```


```{r}
hilbert(m = matrix(1), n = 1, r = 2)
```

```{r}
ggplot() + 
  geom_path(data = hilbert(m = matrix(1), 
                           n = 5, 
                           r = 2), 
            aes(x, y)) + 
  coord_equal()
```

```{r}
ggplot() + 
  geom_path(data = hilbert(m = matrix(-1), 
                           n = 5, 
                           r = 2), 
            aes(x, y),
            color = "red",
            size = 1) +
  geom_polygon(data = hilbert(m = matrix(1), 
                              n = 5, 
                              r = 2), 
               aes(x, y)) + 
  coord_equal()
```

```{r}
hilbert2(matrix(1), n = 1, r = 2)
```

```{r}
h3 <- data.frame(geometry = hilbert(m = matrix(tan(1)), 
                                    n = 4, 
                                    r = 2)[,1:2] %>%
                   as.matrix() %>%
                   st_linestring() %>% 
                   st_geometry()) %>%
  st_sf()

ggplot() +
  geom_sf(data = h3 %>%
            st_buffer(dist = 0.35),
          fill = "blue") +
  geom_sf(data = h3 %>%
            st_buffer(dist = 0.175),
          fill = "red") +
  geom_sf(data = h3,
          color = "white",
          size = 0.35) +
  theme_void()
```

```{r}
h3 <- data.frame(geometry = hilbert(m = matrix(1), 
                                    n = 4, 
                                    r = 2)[,1:2] %>%
                   as.matrix() %>%
                   st_linestring() %>% 
                   st_geometry()) %>%
  st_sf()

ggplot() +
  geom_sf(data = h3 %>%
            st_buffer(dist = 0.35),
          fill = "blue") +
  geom_sf(data = h3 %>%
            st_buffer(dist = 0.175),
          fill = "red") +
  geom_sf(data = h3,
          color = "white",
          size = 0.35) +
  theme_void()
```


```{r}
h3 <- data.frame(geometry = hilbert(m = matrix(3), 
                                    n = 4, 
                                    r = 2)[,1:2] %>%
                   as.matrix() %>%
                   st_linestring() %>% 
                   st_geometry()) %>%
  st_sf()

ggplot() +
  geom_sf(data = h3 %>%
            st_buffer(dist = 0.35),
          fill = "blue") +
  geom_sf(data = h3 %>%
            st_buffer(dist = 0.175),
          fill = "red") +
  geom_sf(data = h3,
          color = "white",
          size = 0.35) +
  theme_void()
```

