---
title: "R Notebook"
output: html_notebook
---

This notebook has some experiments with parametric systems.

Load packages:
```{r}
library(glue)
library(MetBrewer)
library(MexBrewer)
library(tidyverse)
```

First I lifted some code from Antonio Sánchez Chinchón (see here: https://twitter.com/aschinchon/status/1499138667616604168). I modified it to introduce some randomness and the colors are from {MexBrewer}:
```{r eval=FALSE}
seq(-3, 3, by = 0.01) %>%
  expand.grid(x = ., y = .) %>%
  mutate(ex = runif(n(), -0.25, 0.25),
         ey = runif(n()), -0.25, 0.25) %>%
  ggplot(aes(x = (1 - x - sin(y^2) + ex), 
             y = (1 - y - cos(x^2) + ey))) +
  geom_point(aes(color = x * y),
             alpha = 0.05, 
             shape = 20, 
             size = 0)+
  scale_color_gradientn(colors = MexBrewer::mex.brewer("Atentado"))  +
  coord_polar()+
  theme_void() +
  theme(legend.position = "none",
        panel.background = element_rect(color = NA,
                                        fill = "black"))
```

This other chunk introduces more random parameters. (Try with geom_path: it takes much longer to render but the results are interesting):
```{r}
# Set a seed
seed <- sample.int(10000, 1)
set.seed(seed)

# Select a color palette at random
palette_name <- sample(c("Alacena", "Atentado", "Revolucion", "Ronda"), 1)
col_palette <- mex.brewer(palette_name)

# Generate the system and plot
seq(-3, 3, by = 0.01) %>%
  expand.grid(x = ., y = .) %>%
  mutate(ex = runif(n(), -0.25, 0.25),
         ey = runif(n()), -0.25, 0.25,
         x = (sample(c(-1, 1), 1) * runif(n(), 0.5, 2.5) - sample(c(-1, 1), 1)* runif(n(), 0.0, 2.5) * x - sample(c(-1, 1), 1) * sin(y^sample.int(4, 1)) + ex), 
         y = (sample(c(-1, 1), 1) * runif(n(), 0.5, 2.5) - sample(c(-1, 1), 1)* runif(n(), 0.0, 2.5) * y - sample(c(-1, 1), 1) * cos(x^sample.int(4, 1)) + ey)) %>%
  ggplot(aes(x = x, y = y)) +
  geom_point(aes(color = x * y),
             alpha = 0.05, 
             shape = 20, 
             size = 0) +
  scale_color_gradientn(colors = col_palette) +
  coord_polar(start = runif(1, 0, 2 * pi),
              direction = sample(c(-1, 1), 1)) +
  theme_void() +
  theme(legend.position = "none",
        panel.background = element_rect(color = NA,
                                        fill = "black"),
        plot.background = element_rect(color = NA,
                                       fill = "black"))

# Save
#ggsave(glue("par-system-{seed}-{palette_name}.png"),
#       height = 7,
#       width = 7,
#       units = "in")
```


```{r}
# Set a seed
seed <- sample.int(10000, 1)
set.seed(seed)

# Select a color palette at random
palette_name <- sample(c("Aurora", "Concha", "Frida", "Tierra"), 1)#sample(c("Alacena", "Atentado", "Revolucion", "Ronda"), 1)
col_palette <- mex.brewer(palette_name)

# Generate the system and plot
seq(-3, 3, by = 0.01) %>%
  expand.grid(x = ., y = .) %>%
  mutate(ex = runif(n(), -0.25, 0.25),
         ey = runif(n()), -0.25, 0.25,
         x = (sample(c(-1, 1), 1) * runif(n(), 0.5, 1.5) - sample(c(-1, 1), 1) * x - sample(c(-1, 1), 1) * sin(y^sample.int(4, 1)) + ex), 
         y = (sample(c(-1, 1), 1) * runif(n(), 0.5, 1.5) - sample(c(-1, 1), 1) * y - sample(c(-1, 1), 1) * cos(x^sample.int(4, 1)) + ey)) %>%
  ggplot(aes(x = x, y = y)) +
  geom_path(aes(color = x * y),
            alpha = 0.05, 
            size = 0) +
  scale_color_gradientn(colors = col_palette) +
  coord_polar(start = runif(1, 0, 2 * pi),
              direction = sample(c(-1, 1), 1)) +
  theme_void() +
  theme(legend.position = "none",
        panel.background = element_rect(color = NA,
                                        fill = "black"),
        plot.background = element_rect(color = NA,
                                       fill = "black"))

# Save
ggsave(glue("par-system-path-{seed}-{palette_name}.png"),
       height = 7,
       width = 7,
       units = "in")
```

Variation with sequential palettes:
```{r}
# Set a seed
seed <- sample.int(10000, 1)
set.seed(seed)

# Select a color palette at random
palette_name <- sample(c("metbrewer", "mexbrewer"), 1)
if(palette_name == "mexbrewer"){
  palette_name <- sample(c("Aurora", "Concha", "Frida", "Tierra"), 1)
  col_palette <- mex.brewer(palette_name)
  }else{
  palette_name <- sample(c("Cassatt1", "Greek", "Hokusai2", "Hokusai3", "OKeeffe2", "Peru2", "Robert", "VanGogh3"), 1)
  col_palette <- met.brewer(palette_name)
  }

# Generate the system and plot
seq(-3, 3, by = 0.01) %>%
  expand.grid(x = ., y = .) %>%
  mutate(ex = runif(n(), -0.25, 0.25),
         ey = runif(n()), -0.25, 0.25,
         x = (sample(c(-1, 1), 1) * runif(n(), 0.5, 1.5) - sample(c(-1, 1), 1) * x - sample(c(-1, 1), 1) * sin(y^sample.int(4, 1)) + ex), 
         y = (sample(c(-1, 1), 1) * runif(n(), 0.5, 1.5) - sample(c(-1, 1), 1) * y - sample(c(-1, 1), 1) * cos(x^sample.int(4, 1)) + ey)) %>%
  ggplot(aes(x = x, y = y)) +
  geom_path(aes(color = x * y),
            alpha = 0.05, 
            size = 0.1) +
  scale_color_gradientn(colors = col_palette) +
  coord_polar(start = runif(1, 0, 2 * pi),
              direction = sample(c(-1, 1), 1)) +
  theme_void() +
  theme(legend.position = "none",
        panel.background = element_rect(color = NA,
                                        fill = sample(col_palette, 1)),
        plot.background = element_rect(color = NA,
                                       fill = sample(col_palette, 1)))

# Save
ggsave(glue("par-system-path-{seed}-{palette_name}.png"),
       height = 7,
       width = 7,
       units = "in")
```

Here is a different system:
```{r}
df <- #data.frame(t = seq(pi/32, 2 * pi/32, 0.00005)) %>%
  data.frame(t = seq(0, pi, 0.00005)) %>%
  # The first coefficient controls how tightly packed the blobs are; the next two coefficients control ow spread they are horizontally and vertically
  mutate(z = 0.5 * (1i * sin(t * pi) + 1 * cos(t * pi)) 
         # The first coefficient controls the shape of the blobs
         - 0.5 * sin(5 * pi * 0.607) * exp(-1i * 4 * pi * t)
         #- 0.5 * exp(1i * 6 * pi * (t + 0.7))
         #+ 0.1 * exp(1i * 1200 * pi * t) * sin((2.5 * pi * t + pi * 0.607))^10#80 this exponent controls how much overlap there is between lines of the smaller elements of the plot
         # First coeff is
         + 0.4 * exp(1i * 1200 * pi * t) * sin((2.5 * pi * t + pi * 0.107))^10#80 this exponent controls how much overlap there is between lines of the bigger elements of the plot: bigger numbers more overlap - less density
         ) %>%
  mutate(x = Re(z),
         y = Im(z))
```

```{r}
# Select a color palette at random
palette_name <- sample(c("metbrewer", "mexbrewer"), 1)
if(palette_name == "mexbrewer"){
  palette_name <- sample(c("Aurora", "Concha", "Frida", "Tierra"), 1)
  col_palette <- mex.brewer(palette_name)
  }else{
  palette_name <- sample(c("Cassatt1", "Greek", "Hokusai2", "Hokusai3", "OKeeffe2", "Peru2", "Robert", "VanGogh3"), 1)
  col_palette <- met.brewer(palette_name)
  }

a1 <- runif(1, 0.25, 1.25)
a2 <- runif(1, 0.25, 1.25)
a3 <- runif(1, 0.25, 1.25)

xp <- sample.int(100, 1)

#df <- #data.frame(t = seq(pi/32, 2 * pi/32, 0.00005)) %>%
  data.frame(t = seq(0, pi, 0.00005)) %>%
  # The first coefficient controls how tightly packed the blobs are; the next two coefficients control ow spread they are horizontally and vertically
  mutate(z = a1 * (1i * sin(t * pi) + 1 * cos(t * pi)) 
         # The first coefficient controls the shape of the blobs
         - a2 * sin(5 * pi * 0.607) * exp(-1i * 4 * pi * t)
         #- 0.5 * exp(1i * 6 * pi * (t + 0.7))
         #+ 0.1 * exp(1i * 1200 * pi * t) * sin((2.5 * pi * t + pi * 0.607))^10#80 this exponent controls how much overlap there is between lines of the smaller elements of the plot
         # First coeff is
         + a3 * exp(1i * 1200 * pi * t) * sin((2.5 * pi * t + pi * 0.107))^xp#80 this exponent controls how much overlap there is between lines of the bigger elements of the plot: bigger numbers more overlap - less density
         ) %>%
  mutate(x = Re(z),
         y = Im(z)) %>%
  ggplot(aes(x = x, y = y)) +
  geom_path(aes(color = x * y,
            size = x * y),
            alpha = 0.5) +
  scale_color_gradientn(colors = col_palette) +
  # coord_polar(start = runif(1, 0, 2 * pi),
  #             direction = sample(c(-1, 1), 1)) +
  scale_size(range = c(0.1, 0.75)) +
  coord_equal() +
  theme_void() +
  theme(legend.position = "none",
        panel.background = element_rect(color = NA,
                                        fill = sample(col_palette, 1)),
        plot.background = element_rect(color = NA,
                                       fill = sample(col_palette, 1)))
  
# Save
ggsave(glue("parametric-balls-{palette_name}-{seed}.png"),
       height = 7,
       width = 7,
       units = "in")  
```



